Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-07 sections/observations.tex
Added optical lightcurve comparion image

By stacking the lightcurves, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.

@@

>>>>

By stacking the lightcurves [\ref{fig:OpticalLightcurveComparison}], we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.

@@

    \includegraphics[width=0.5\textwidth]{figures/OpticalLightcurveComparison}
    \caption{\label{fig:OpticalLightcurveComparison} A comparison of the livestream, light sensor, and \texttt{Stellarium} lightcurves.}
